---
title: "The Compass R Package"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What is the `compass` R package?

The `compass` R package is a toy package made by [Mauro Camara Escudero](https://github.com/MauroCE) for the personal portfolio of the [Statistical Computing 1](https://awllee.github.io/sc1-2019/) course delivered by [Anthony Lee](http://www.bristol.ac.uk/maths/people/anthony-w-lee/index.html) to first year PhD students in [Computational Statistics and Data Science](COMPASS) at the [University of Bristol](www.bris.ac.uk). What you are seeing now is an RMarkdown file that is part of the package repository and is deployed by [Travis CI](https://travis-ci.com) on [GitHub Pages](https://pages.github.com/).

### Installation

You can install the development version from [GitHub](https://github.com/) with:
``` r
# install.packages("devtools")
devtools::install_github("MauroCE/compass")
```

### Examples
The `compass` package is extremely powerful and flexible, so the following examples are here only to give a taster of its full capabilities. With the `compass` package we can sum the squares of two numbers

```{r importing library}
# Attach the package
library(compass)
# Find the sum of the squares of two numbers
z <- sumsquares(2, 4)
z
```
and transpose the head of a dataframe
```{r tilt}
# and tilt the head of a dataframe
df <- data.frame(matrix(1:30, 10, 3))
tilted_head <- tilt_head(df, 3)
```
and that's it.


## License
This project is licensed under the terms of the MIT license. 
The full license can be found [here](LICENSE.md).
