---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# compass
<!-- badges: start -->
[![Build Status](https://travis-ci.com/MauroCE/compass.svg?branch=master)](https://travis-ci.com/MauroCE/compass)
[![codecov](https://codecov.io/gh/MauroCE/compass/branch/master/graph/badge.svg)](https://codecov.io/gh/MauroCE/compass)
<!-- badges: end -->

The goal of compass is to exemplify a toy R package for the personal portfolio of the Statistical Computing 1 course attended by first year PhD students in Computational Statistics and Data Science (COMPASS) at the University of Bristol.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("MauroCE/compass")
```
## Example

This is a basic example which shows how to use the compass package.

```{r example}
# Attach the package
library(compass)
# Find the sum of the squares of two numbers
z <- sumsquares(2, 4)
# and tilt the head of a dataframe
df <- data.frame(matrix(1:30, 10, 3))
tilted_head <- tilt_head(df, 3)
```
we can check the output 
```{r example_output}
z
```
and 
```{r example_output2}
tilted_head
```

## License
This project is licensed under the terms of the MIT license. 
The full license can be found [here](LICENSE.md).
